### 2021-07-14 chapters/rq2/1_experiment_design.tex
Updates from Overleaf

\subsubsection{Neural gas}
The neural gas is a topology-preserving network, and can be treated as an extension to the C-means\cite{Du2010Clustering:Approach}.
A data optimal topological ordering is achieved by using neighborhood ranking within the input space at each training step\cite{Du2010Clustering:Approach}.
To find its neighborhood rank, each neuron compares its distance to the input vector with those of all the other neurons to the input vector\cite{Du2010Clustering:Approach}. 
Unlike the \acrfull{som}(see Chapter \ref{ch:topThreeModels}, which uses predefined static neighborhood relations, the neural gas network determines a dynamical neighborhood relation as learning proceeds\cite{Du2010Clustering:Approach}.
A benefit of the neural gas network is that it is able to spawn neurons.
This means that it is not necessary to know the number of clusters in advance.
Unfortunately the neural gas network is a learning network.
One of the properties of a learning network is that it is not designed to fit new data points\cite{supervisedUnsupervised}.
For this reason we cannot use the neural gas network to predict in what cluster a new mutant should be placed.
Therefore we will not select the neural gas network.

>>>>

\subsubsection{Neural gas}
The neural gas is a topology-preserving network, and can be treated as an extension to the C-means\cite{Du2010Clustering:Approach}.
A data optimal topological ordering is achieved by using neighborhood ranking within the input space at each training step\cite{Du2010Clustering:Approach}.
To find its neighborhood rank, each neuron compares its distance to the input vector with those of all the other neurons to the input vector\cite{Du2010Clustering:Approach}. 
Unlike the \acrlong{som}(see Chapter \ref{ch:topThreeModels}, which uses predefined static neighborhood relations, the neural gas network determines a dynamical neighborhood relation as learning proceeds\cite{Du2010Clustering:Approach}.
A benefit of the neural gas network is that it is able to spawn neurons.
This means that it is not necessary to know the number of clusters in advance.
Unfortunately the neural gas network is a learning network.
One of the properties of a learning network is that it is not designed to fit new data points\cite{supervisedUnsupervised}.
For this reason we cannot use the neural gas network to predict in what cluster a new mutant should be placed.
Therefore we will not select the neural gas network.
